---
title: "data-acquisition"
author: "Andrew.Z.Flores"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
# Install packages (uncomment to install)
#install.packages("childesr")

# Load required libraries
library(childesr)  # Required to download CHILDES transcripts
library(tidyverse) # Required for data manipulation
library(here)
```


# Data Acquisition
## Child Vocabulary Data
### Mac Arthur Bates Communicative Inventories (MCDI)

Download the MCDI dataset by accesing the wordbank website. Under `data`, select the Full Child-by-Word Data. Doing so will initate a download of the full mcdi dataset. We have saved this dataset to the data file. 

### Child Language Data Exchange System (CHILDES)
Next we will download all English (American) transcripts using the *childesr*
package. This is a large file and make take 5 minutes or so to download.
```{r, download_childes}
# Download CHILDES utterances
childes_data_raw <- get_utterances(collection = "Eng-NA")

# Select relevant columns
childes_data_select <- childes_data_raw %>%
  select(id,
         target_child_age,
         gloss,
         type,
         speaker_code,
         speaker_role,
         collection_name,
         transcript_id)

# transcript information
childes_transcripts <- get_transcripts()

```

```{r}
#Create data file structure
data_folder <- here("data")
if (!dir.exists(data_folder)) {
  dir.create(data_folder)
}

# Save data frames to CSV files
write.csv(childes_data_raw, file = here("data","raw_childes.csv"), row.names = FALSE)
write.csv(childes_data_select, file = here("data", "select_childes.csv"), row.names = FALSE)
write.csv(childes_transcripts, file = here("data", "childes transcripts.csv"), row.names = FALSE)
```



