---
title: "Inferential Graphs"
author: "Andrew.Z.Flores"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(lme4)
library(lmerTest)
library(here)
library(tidyverse) 
library(jtools)
library(broom.mixed)

```

# Set the working directory
```{r}
# Set the working directory
folder_path <- here("R_Objects")
setwd(folder_path)

# List all .Rdata files in the folder
data_files <- list.files(pattern = "\\.Rdata$")

# Load each .Rdata file
for (file in data_files) {
  load(file)
}

```

# Create a function to calculate the statistics for Single_Model_Estimates 

```{r}
# List the model objects and their names
models <- list(model8.0 = model8.0, model8.1 = model8.1, model8.2 = model8.2, model8.3 = model8.3,
                model9.0 = model9.0, model9.1 = model9.1, model9.2 = model9.2, model9.3 = model9.3,
                model10.0 = model10.0, model10.1 = model10.1, model10.2 = model10.2, model10.3 = model10.3,
                model11.0 = model11.0, model11.1 = model11.1, model11.2 = model11.2, model11.3 = model11.3,
                model12.0 = model12.0, model12.1 = model12.1, model12.2 = model12.2, model12.3 = model12.3)

# List the model objects and their corresponding fixed effects
models_and_effects <- list(model8.0 = "FQ_scaled", model8.1 = "LD_scaled", model8.2 = "DD_scaled", model8.3 = "PKC_scaled",
                           model9.0 = "FQ_scaled", model9.1 = "LD_scaled", model9.2 = "DD_scaled", model9.3 = "PKC_scaled",  # Corrected here
                           model10.0 = "FQ_scaled", model10.1 = "LD_scaled", model10.2 = "DD_scaled", model10.3 = "PKC_scaled",
                           model11.0 = "FQ_scaled", model11.1 = "LD_scaled", model11.2 = "DD_scaled", model11.3 = "PKC_scaled",
                           model12.0 = "FQ_scaled", model12.1 = "LD_scaled", model12.2 = "DD_scaled", model12.3 = "PKC_scaled")


# Mapping model numbers to age categories
age_mapping <- list(model8.0 = 18, model8.1 = 18, model8.2 = 18, model8.3 = 18,
                    model9.0 = 21, model9.1 = 21, model9.2 = 21, model9.3 = 21,
                    model10.0 = 24, model10.1 = 24, model10.2 = 24, model10.3 = 24,
                    model11.0 = 27, model11.1 = 27, model11.2 = 27, model11.3 = 27,
                    model12.0 = 30, model12.1 = 30, model12.2 = 30, model12.3 = 30)


# Function to extract the statistics from a model
get_stats <- function(model, fixed_effect_name) {
  coefs <- summary(model)$coefficients
  if (!fixed_effect_name %in% rownames(coefs)) {
    warning(paste("Fixed effect", fixed_effect_name, "not found in model. Returning NA."))
    return(rep(NA, 6))  # return NAs for all values if fixed effect is not found
  }
  fixed_effects <- coefs[fixed_effect_name, ]
  p_value <- 2 * pnorm(-abs(fixed_effects["z value"])) # Two-tailed p-value
  
  return(c(
    LogOdds = fixed_effects["Estimate"],
    SE = fixed_effects["Std. Error"],
    z = fixed_effects["z value"],
    P = p_value,
    CI_low = fixed_effects["Estimate"] - 1.96 * fixed_effects["Std. Error"],
    CI_high = fixed_effects["Estimate"] + 1.96 * fixed_effects["Std. Error"]
  ))
}

# Calculate the statistics for each model
stats_list <- mapply(get_stats, models, models_and_effects, SIMPLIFY = FALSE, USE.NAMES = TRUE)
 
# Combine the statistics into a data frame
stats_df <- do.call(rbind, stats_list)

# Convert to a data frame
stats_df <- data.frame(stats_df)

# Add an 'Age' column to store the corresponding age categories
stats_df$Age <- plyr::mapvalues(rownames(stats_df), names(age_mapping), age_mapping)

# Ensure age is treated as a numeric variable
stats_df$Age <- as.numeric(stats_df$Age)

# Add row names as a new column 'Model'
stats_df$Model <- rownames(stats_df)

# Add a 'Predictor' column to store the corresponding predictor effects
stats_df$Predictor <- plyr::mapvalues(rownames(stats_df), names(models_and_effects), models_and_effects)

# Rename the columns to match the desired output
names(stats_df) <- c("Estimate", "Std. Error", "z-value", "Pr(>|z|)", "2.50%", "97.50%", "Age", "Model", "Predictor")

# Reorder the dataframe by Predictor and Age
stats_df <- stats_df %>% dplyr::arrange(Predictor, Age)

# Reset row names
rownames(stats_df) <- NULL

# View the data frame
print(stats_df)
```

```{r}
# Unlist the predictor variable
stats_df$Predictor <- unlist(stats_df$Predictor)

# Convert the predictor variable to a factor
stats_df$Predictor <- as.factor(stats_df$Predictor)

# Define the desired order of predictors
predictor_order <- c("Frequency", "Lexical Diversity", "Document Diversity", "Pro-KWo")

# Define the desired order of ages
age_order <- c(18, 21, 24, 27, 30)

# Reorder the levels of the age factor to match the desired order
stats_df$Age <- factor(stats_df$Age, levels = age_order)

# Reorder the rows of the data frame based on the new order of the predictor and age factors
stats_df <- stats_df[order(stats_df$Predictor, stats_df$Age), ]

# If needed, reorder columns of the data frame
desired_column_order <- c("Predictor", "Age", "Estimate", "Std. Error", "z-value", "Pr(>|z|)", "2.50%", "97.50%")
stats_df <- stats_df[, desired_column_order] 

# Use the recode function to change "PKC_Scaled" to "PKC_scaled"
stats_df$Predictor <- recode(stats_df$Predictor, "PKC_Scaled" = "PKC_scaled")


# change all number to 3 decimal places
stats_df$Estimate <- round(stats_df$Estimate, digits = 3)
stats_df$`Std. Error` <- round(stats_df$`Std. Error`, digits = 3)
stats_df$`z-value` <- round(stats_df$`z-value`, digits = 3)
stats_df$`Pr(>|z|)` <- round(stats_df$`Pr(>|z|)`, digits = 3)
stats_df$`2.50%` <- round(stats_df$`2.50%`, digits = 3)
stats_df$`97.50%` <- round(stats_df$`97.50%`, digits = 3)

# Save the summary_df to a CSV
write.csv(stats_df, file = here("figures_&_tables","Table5_Single_Model_Estimates.csv"),row.names = F)

```

# Figure 3
```{r}

# Convert the Age variable to a factor
stats_df$Age <- as.factor(stats_df$Age)

figure3_data <- ggplot(data=stats_df, 
                       aes(x = Age,
                           y = Estimate, 
                           group = Predictor)) +
  geom_pointrange(aes(color = Predictor), ymin = stats_df$`2.50%`, ymax= stats_df$`97.50%`, size = 1, linetype = 1) +
  geom_line(aes(color = Predictor), size = 2,linetype = 6) +
  geom_point(aes(color = Predictor), size = 2) +
  scale_color_manual(values = c("#eeb1a2","#02a699","#f45c51","#274dc6"), labels = c("Document Diversity", "Frequency", "Lexical Diversity", "Pro-KWo")) +
  labs(x = "Age (mo)" , y = "Estimate Value") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        panel.spacing.x = unit(1.5,"lines"),
        strip.background = element_rect(fill = "#00539CFF"),
        strip.text = element_text(colour = "#FFD662FF"),
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA), 
        text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 20, face = "bold")) +
  geom_hline(yintercept=0,linetype=2) +
  theme(text = element_text(size=25, hjust = 0.5), legend.position = "top", legend.title = element_blank())

# Save the figure
ggsave(filename = here("figures_&_tables", "Figure 3. Single_Model_Estimates.jpeg"), plot = figure3_data, width = 11, height = 14)
```
# Create a function to calculate the statistics for Two_Model_Estimates  
```{r}
# List the model objects and their names models 13 to 27
models <- list(model13 = model13,model14 = model14,model15 = model15,model16 = model16,model17 = model17,
                model18 = model18,model19 = model19,model20 = model20,model21 = model21,model22 = model22,
                model23 = model23,model24 = model24,model25 = model25,model26 = model26,model27 = model27)

models_and_effects <- list(model13 = c("FQ_scaled", "PKC_scaled"), model14 = c("FQ_scaled", "PKC_scaled"), model15 = c("FQ_scaled", "PKC_scaled"), model16 = c("FQ_scaled", "PKC_scaled"),model17 = c("FQ_scaled", "PKC_scaled"),
                           model18= c('LD_scaled', 'PKC_scaled'), model19= c('LD_scaled', 'PKC_scaled'), model20= c('LD_scaled', 'PKC_scaled'), model21= c('LD_scaled', 'PKC_scaled'), model22= c('LD_scaled', 'PKC_scaled'),
                           model23= c('DD_scaled', 'PKC_scaled'), model24= c('DD_scaled', 'PKC_scaled'), model25= c('DD_scaled', 'PKC_scaled'), model26= c('DD_scaled', 'PKC_scaled'), model27= c('DD_scaled', 'PKC_scaled'))

# Mapping model numbers to age categories

age_mapping <- list(model13 = 18, model14 = 21, model15 = 24, model16 = 27,model17= 30,
                    model18 = 18, model19 = 21, model20 = 24, model21 = 27,model22= 30,
                    model23 = 18, model24 = 21, model25 = 24, model26 = 27,model27= 30)

                    # Function to extract the statistics from a model (now handles multiple predictors)
get_stats <- function(model, fixed_effect_names) {
  # Initialize an empty list to store stats for each predictor
  stats_list <- list()
  
  # For each predictor...
  for (fixed_effect_name in fixed_effect_names) {
    coefs <- summary(model)$coefficients
    
    # If the predictor is not found in the model, issue a warning and skip to the next predictor
    if (!fixed_effect_name %in% rownames(coefs)) {
      warning(paste("Fixed effect", fixed_effect_name, "not found in model. Skipping this effect."))
      next
    }
  
    fixed_effects <- coefs[fixed_effect_name, ]
    p_value <- 2 * pnorm(-abs(fixed_effects["z value"])) # Two-tailed p-value
  
    stats <- c(
      LogOdds = fixed_effects["Estimate"],
      SE = fixed_effects["Std. Error"],
      z = fixed_effects["z value"],
      P = p_value,
      CI_low = fixed_effects["Estimate"] - 1.96 * fixed_effects["Std. Error"],
      CI_high = fixed_effects["Estimate"] + 1.96 * fixed_effects["Std. Error"],
      Predictor = fixed_effect_name  # Store predictor name as part of stats
    )
  
    # Append the stats to the list
    stats_list[[fixed_effect_name]] <- stats
  }
  
  return(stats_list)
}

# Calculate the statistics for each model and predictor
stats_list <- mapply(get_stats, models, models_and_effects, SIMPLIFY = FALSE, USE.NAMES = TRUE)

# Flatten the list of statistics into a data frame
stats_df <- do.call(rbind, unlist(stats_list, recursive = FALSE))

# Convert to a data frame
stats_df <- data.frame(stats_df)

# Add an 'Age' column to store the corresponding age categories
stats_df$Age <- plyr::mapvalues(rownames(stats_df), names(age_mapping), age_mapping)

# Ensure age is treated as a numeric variable
stats_df$Age <- as.numeric(stats_df$Age)

# Add row names as a new column 'Model'
stats_df$Model <- gsub("\\..*$", "", rownames(stats_df))  # Extract model name before the "." in row names

# Rename the columns to match the desired output
names(stats_df) <- c("Estimate", "Std. Error", "z-value", "Pr(>|z|)", "2.50%", "97.50%", "Predictor", "Age", "Model")

# Update Age column based on Model column
stats_df$Age <- plyr::mapvalues(stats_df$Model, names(age_mapping), age_mapping)

# Reorder the dataframe by Predictor and Age
stats_df <- stats_df %>% dplyr::arrange(Predictor, Age)

# Reset row names
rownames(stats_df) <- NULL

# View the data frame
print(stats_df)


# Unlist the "Age" column
stats_df$Age <- unlist(stats_df$Age)

# identify numeric columns and change to 3 decimal places


# Save stats_df to csv file
write.csv(stats_df, file = here("figures_&_tables","Table 6. Two Predictor Models.csv"),row.names = F)



```

# Create table for Two_Model_Estimates
```{r}
library(knitr)

# Create groups for each Age
groups <- unique(stats_df$Age)

# For each group, create a sub-table
for (age in groups) {
  df <- stats_df[stats_df$Age == age, ]
  
  # Print the age
  cat(paste0(age, "\n"))
  
  # Print the table
  print(kable(df[, c("Predictor", "Estimate", "Std. Error", "z-value", "Pr(>|z|)", "2.50%", "97.50%")], 
               row.names = FALSE, 
               col.names = c("Predictor", "Estimate", "Std. Error", "z-value", "p-value", "2.50%", "97.50%"),
               format = "markdown"))
}

``` 

# Create a summary table of Age * Predictor models.
```{r}
# Define a function to generate summary from a model
model_summary <- function(model, predictor){
  # Generate summary dataframe and add Model column
  summary <- broom.mixed::tidy(model) %>% 
              select(term, estimate, std.error, statistic, p.value) %>% 
              mutate(conf.low = estimate - 1.96*std.error,
                     conf.high = estimate + 1.96*std.error) %>%
              rename(Factor = term,
                     LogOdds = estimate,
                     SE = std.error,
                     z = statistic,
                     `P(>|z|)` = p.value,
                     `2.5%` = conf.low,
                     `97.5%` = conf.high) %>%
              mutate(Model = paste0("Model_", predictor))
  return(summary)
}

# Load models
load("R_Objects/model28.Rdata")
load("R_Objects/model29.Rdata")
load("R_Objects/model30.Rdata")
load("R_Objects/model31.Rdata")

# Create a list of models and their respective predictor names
models_list <- list(model28 = "FQ_scaled", model29 = "LD_scaled", model30 = "DD_scaled", model31 = "PKC_scaled")

# Initialize an empty data frame for storing summaries
summary_df <- data.frame()

# Iterate over models and append their summaries to the summary_df
for(i in 1:length(models_list)){
  model <- get(names(models_list)[i])
  predictor <- models_list[[i]]
  summary <- model_summary(model, predictor)
  summary_df <- rbind(summary_df, summary)
}

# Save the summary_df to a CSV
write.csv(summary_df, file = here("figures_&_tables","interaction_models.csv"),row.names = F)
``` 

# Figure 7 Correlation of MCDIp with predicted model probabilities at 24 months. Positive values along the x-axis represent over predictions, while negative values represent under predicted values.
## Load model (model32)
## Create a dataframe of predicted probabilities
```{r}
# Load the saved model
load(file = here("R_Objects", "model32.Rdata"))
model32_subset <- regression_dataset %>% filter(age == 24)


# Ensure "word" and "MCDIp" columns are included in the data
model32_subset <- model32_subset %>% select(word, MCDIp, everything())

# Generate model probabilities
model32_subset$predicted_probabilities <- predict(model32, newdata = model32_subset, type = "response", re.form = NA)


model32_results <- model32_subset %>%
    select(word, MCDIp, predicted_probabilities) %>%
    distinct()

word_stats <- read.csv(file = here('data','target_words.csv'))


model32_results <- full_join(model32_results,word_stats)

model32_results <- model32_results %>% mutate(`(MCDIp-Predicted
                                                Probability)`= predicted_probabilities-MCDIp)
                                               
                                               model32_results <- model32_results %>%
  mutate(lexical_class = recode(lexical_class,
                                'function_words' = 'Function',
                                'verbs' = 'Verbs',
                                'nouns' = 'Nouns',
                                'adjectives' = 'Adjectives'))

```

```{r}
Residuals_Plot.24 <- model32_results %>%
  ggplot(aes(x = `(MCDIp-Predicted
                                                Probability)`, y = MCDIp, fill = lexical_class, label = word)) +
  geom_label(size = 5, alpha = 0.6) +
  stat_smooth(method = 'lm', se = TRUE, color = "black", aes(group = lexical_class, color = lexical_class)) +
  scale_fill_manual(labels =c("Adjectives","Function", "Nouns","Verbs"), 
                    values = c("#ffd125","#6fafc7","#bfd46d","#ee5e5e")) +
  theme_bw() +
  labs(x = "MCDIp - Predicted Probability", y = "MCDIp") +
  theme(legend.position = "top", 
        legend.title = element_blank(), 
        legend.text = element_text(size = 20, face = "bold"),
        axis.title.x=element_text(size = 20, face = "bold"),
         axis.title.y=element_text(size = 20, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),
        strip.background = element_rect(fill = "#00539CFF" ) ,
        strip.text = element_text(colour = "#FFD662FF", size = 28, face = "bold" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold"))

ggsave(Residuals_Plot.24, file = here('figures_&_tables',"Figure7.Residuals.jpeg"), dpi = "retina", width = 17, height = 15)


s <- MCDIp_unique %>% filter(age == 30) 


```



