---
title: "Data Cleaning"
author: "Andrew.Z.Flores"
date: "`r Sys.Date()`"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(GGally)
library(RColorBrewer)
library(corrplot)
library(here)
library(data.table)
library(ggplot2)
library(gghalves)
library(ggrepel)
library(ggpubr)
library(gt)
library(grDevices)
library(kableExtra)
library(knitr)
library(lattice)
library(readr)
library(reshape2)
library(tidyverse)
library(viridis)
```


```{r}
#Create figures data file structure
data_folder <- here("figures_&_tables")
if (!dir.exists(data_folder)) {
  dir.create(data_folder)
}


#Create suplementary figure data file structure
data_folder <- here("supplemental material")
if (!dir.exists(data_folder)) {
  dir.create(data_folder)
}
```


#Load Data
```{r, setup, include=FALSE}
plotting_dataset <- fread(here("data", "plotting_dataset.csv"), colClasses = c("factor","factor","factor","numeric","numeric","numeric","numeric","numeric"))

```

# Tables
## Table 2
```{r}
# Define a helper function to calculate a correlation matrix and reshape it into a data frame
correlation_to_dataframe <- function(df) {
  cor_matrix <- cor(df[, c("log_FQ", "LD", "DD", "PKC")])
  cor_df <- as.data.frame(as.table(cor_matrix))
  names(cor_df) <- c("predictor1", "predictor2", "correlation")
  cor_df
}

# Apply the function to each age
correlation_results <- plotting_dataset %>%
  group_by(age) %>%
  do(correlation_to_dataframe(.))

# Filter out the correlations of predictors with themselves
correlation_results <- correlation_results %>%
  filter(predictor1 != predictor2)

# Reshape the data to the final format
final_correlation_table <- correlation_results %>%
  spread(predictor1, correlation)

# View the final table
print(final_correlation_table)
```

 
```{r}
# Write the final correlation table to a CSV file 
ages <- c(18,21,24,27,30)
final_correlation_table_sub <- final_correlation_table %>% filter(age %in% ages)
write.csv(final_correlation_table_sub, file = here("figures_&_tables", "Table 2.csv"),row.names = F)
write.csv(final_correlation_table, file = here("supplemental material", "Table 2_All.csv"),row.names = F)
```
 

## Table 3
```{r}
# Function to calculate correlations between age groups
correlation_between_ages <- function(df1, df2) {
  cor(df1, df2, use = "pairwise.complete.obs", method = "pearson")
}

# Compute the correlations for each predictor across ages
correlations_all <- data.frame()
predictors <- c("MCDIp", "log_FQ", "LD", "DD", "PKC")

for (predictor in predictors) {
  for (age1 in unique(plotting_dataset$age)) {
    for (age2 in unique(plotting_dataset$age)) {
      correlation_value <- correlation_between_ages(
        subset(plotting_dataset, age == age1)[[predictor]],
        subset(plotting_dataset, age == age2)[[predictor]])
      
      correlations_all <- rbind(correlations_all, 
                                data.frame(predictor = predictor,
                                           age1 = age1,
                                           age2 = age2,
                                           correlation = correlation_value))
    }
  }
}

# Print the correlation_by_age_all dataframe
print(correlations_all)

# Write the correlation_by_age_all dataframe to a CSV file in the supplemental material folder
write.csv(correlations_all, file = here("supplemental material", "Table 3_All.csv"), row.names = F)

# Now filter out the specific ages of interest
ages <- c(18,21,24,27,30)  # Define the ages of interest
correlation_by_age <- correlations_all %>% 
  filter(age1 %in% ages)

# Print the correlation_by_age dataframe
print(correlation_by_age)

# Write the correlation_by_age dataframe to a CSV file in the figures & tables folder
write.csv(correlation_by_age, file = here("figures_&_tables", "Table 3.csv"), row.names = F)



```
 
 
 
 
 
 
 
 
# Heat Maps
## Predictor Correlation Matrix Across 5 ages.
```{r message=FALSE, warning=FALSE}
# Calculate correlations and store in a data frame
correlations <- plotting_dataset %>%
  filter(age %in% c(18, 21, 24, 27, 30)) %>%
  group_by(age) %>%
  summarize(Frequency_LexicalDiversity = cor(log_FQ, LD),
            Frequency_DocumentDiversity = cor(log_FQ, DD),
            Frequency_ProKWo = cor(log_FQ, PKC),
            LexicalDiversity_DocumentDiversity = cor(LD, DD),
            LexicalDiversity_ProKWo = cor(LD, PKC),
            DocumentDiversity_ProKWo = cor(DD, PKC)) %>%
  pivot_longer(cols = -age, names_to = "Measure", values_to = "Correlation")

# Convert age column to numeric and create a factor with all levels
correlations$age <- as.numeric(as.character(correlations$age))
age_min <- min(correlations$age)
age_max <- max(correlations$age)
correlations$age <- factor(correlations$age, levels = age_min:age_max)

# Create heatmap of correlations with diverging color scale and contour lines
heatmap_plot <- ggplot(correlations, aes(x = age, y = Measure, fill = Correlation)) +
  geom_tile(color = "white", size = 0.1) +
  geom_text(aes(label = format(round(Correlation, 2), nsmall = 2)), size = 5) +
  geom_contour(aes(z = Correlation), bins = 5, color = "white", size = 0.5) +
  scale_fill_gradientn(name = "Correlation", colours = RColorBrewer::brewer.pal(9, "RdBu"), 
                     limits = c(-1, 1), na.value = "grey50") +
  labs(x = "age", y = NULL) +
  theme(plot.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        axis.title = element_text(size = rel(1.2))) +
  coord_fixed(ratio = 0.5) +
  scale_x_discrete()

# Save the plot as an image
ggsave(file = here("supplemental material","Predictor_Heatmap_Across_5Ages.png"), plot = heatmap_plot, width = 15, height = 8, dpi = "retina")
```

## Predictor Correlation Matrix Across all ages.
```{r message=FALSE, warning=FALSE}
# Calculate correlations and store in a data frame
correlations_all <- plotting_dataset %>%
  group_by(age) %>%
  summarize(Frequency_LexicalDiversity = cor(log_FQ, LD),
            Frequency_DocumentDiversity = cor(log_FQ, DD),
            Frequency_ProKWo = cor(log_FQ, PKC),
            LexicalDiversity_DocumentDiversity = cor(LD, DD),
            LexicalDiversity_ProKWo = cor(LD, PKC),
            DocumentDiversity_ProKWo = cor(DD, PKC)) %>%
  pivot_longer(cols = -age, names_to = "Measure", values_to = "Correlation")

# Convert age column to numeric and create a factor with all levels
correlations_all$age <- as.numeric(as.character(correlations_all$age))
age_min <- min(correlations_all$age)
age_max <- max(correlations_all$age)
correlations_all$age <- factor(correlations_all$age, levels = age_min:age_max)

# Create heatmap of correlations with diverging color scale and contour lines
heatmap_plot_all <- ggplot(correlations_all, aes(x = age, y = Measure, fill = Correlation)) +
  geom_tile(color = "white", size = 0.1) +
  geom_text(aes(label = format(round(Correlation, 2), nsmall = 2)), size = 5) +
  geom_contour(aes(z = Correlation), bins = 5, color = "white", size = 0.5) +
  scale_fill_gradientn(name = "Correlation", colours = RColorBrewer::brewer.pal(9, "RdBu"), 
                     limits = c(-1, 1), na.value = "grey50") +
  labs(x = "age", y = NULL) +
  theme(plot.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        axis.title = element_text(size = rel(1.2))) +
  coord_fixed(ratio = 0.5) +
  scale_x_discrete()


# Save the plot as an image
ggsave(file = here("supplemental material","Predictor_Heatmap_Across_ALLAges.png"), plot = heatmap_plot_all, width = 15, height = 3, dpi = "retina")
```

# Scatterplots
## Figure 1. Correlation of MCDIp and statistical predictors at 24 months.

```{r, Figure_1}
Figure1_data <- plotting_dataset %>% 
  filter(age == "24") %>% 
  select(log_FQ, LD, DD,PKC)

colnames(Figure1_data) <- c("Frequency",
                            "Lexical Diversity",
                            "Document Diversity","Pro-KWo")

Fig1_plot <- ggpairs(Figure1_data,columns= c("Frequency","Lexical Diversity","Document Diversity","Pro-KWo") 
                        ,upper = list(continuous = wrap('cor', size = 8))) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(1.5,"lines"),
        plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#00539CFF" ),
        strip.text = element_text(colour = "#FFD662FF" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA)
        , text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold"))

ggsave(plot = Fig1_plot,file = here("figures_&_tables","Figure1.Correlogram of all distributional statistics at 24 months..png"), width = 17, height = 16, dpi = "retina")
```

## Figure 1S. Correlation of MCDIp and statistical predictors at ALL months.

```{r}
Fig1S_plot <- plotting_dataset %>% 
  select(age, LD, DD, log_FQ, PKC) %>% 
  rename(Frequency = log_FQ, "Lexical Diversity" = LD, "Document Diversity" = DD, "Pro-KWo" = PKC) %>% 
  ggpairs(columns = c("Frequency", "Lexical Diversity", "Document Diversity", "Pro-KWo"),
          mapping = aes(color = as.factor(age)),
          upper = list(continuous = wrap('cor', size = 6, cex = 2, text_args = list(parse = TRUE, fontface = "bold"))),
          cor_args = list(method = "pearson", use = "complete.obs")) +
  
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(1.5,"lines"),
        plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#00539CFF" ),
        strip.text = element_text(colour = "#FFD662FF" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA),
        text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold"))

ggsave(plot = Fig1S_plot,here("supplemental material", "Figure 1S. Correlogram ALL.png"), width = 17, height = 16)


```

## Figure 2. Correlation of Distributional Predictors and MCDIp Across age 
```{r, age by Predictor Density Plot Matrix}

Figure2_data <- plotting_dataset %>% 
  filter(age %in% c(18,21,24,27,30)) %>% 
  select(age, MCDIp, LD, DD, log_FQ, PKC)

colnames(Figure2_data) <-c("age",
                           "MCDIp",
                           "Lexical Diversity",
                           "Document Diversity",
                           "Frequency",
                           "Pro-KWo")

figure2_data <-  Figure2_data %>% 
  gather(key = "Predictor", value =  "Predictor Value", `Lexical Diversity`:`Pro-KWo`)

figure2_data$Predictor = factor(figure2_data$Predictor, 
                                levels=c("Frequency", "Lexical Diversity",
                                         "Document Diversity", "Pro-KWo"))

age_Predictor_Matrix.plot <- figure2_data %>% 
  ggplot(aes(x = `Predictor Value`, y = MCDIp, color = Predictor)) + 
  geom_point(shape = 1)

age_Predictor_Matrix.plot <- age_Predictor_Matrix.plot + 
  facet_grid(vars(age), vars(Predictor), scales = "free_x")

age_Predictor_Matrix.plot <- age_Predictor_Matrix.plot + theme_bw() + 
  theme(legend.position= "none",
        text = element_text(size=30, face = "bold", hjust = 0.5))

age_Predictor_Matrix.plot <- age_Predictor_Matrix.plot + 
  scale_color_manual(values = c("#eeb1a2","#02a699","#f45c51","#274dc6"))

age_Predictor_Matrix.plot <- age_Predictor_Matrix.plot +
    theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing.x = unit(1.5,"lines"),
        plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#00539CFF"),
        strip.text = element_text(colour = "#FFD662FF"),
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA),
        text = element_text(size=28, face = "bold", hjust = 0.5),
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold"))  + 
  geom_smooth(method = lm, se = TRUE, show.legend = TRUE, fill = "lightgray") + 
  ylim(0, 1)

age_Predictor_Matrix.plot <- age_Predictor_Matrix.plot + 
  stat_cor(method = "pearson", color = "black", size = 7, digits = 2)

ggsave(age_Predictor_Matrix.plot,
       file = here("figures_&_tables", "Figure 2. MCDIp by Predictor and age.png"),
       dpi = "retina",
       width = 15, height = 15)

```

## Figure 2S. Correlation of Distributional Predictors and MCDIp Across all ages
```{r, age by Predictor Density Plot Matrix}

Figure2S_data <- plotting_dataset %>% 
  select(age,MCDIp,LD, DD, log_FQ, PKC)

colnames(Figure2S_data) <-c("age",
                           "MCDIp",
                           "Lexical Diversity",
                           "Document Diversity",
                           "Frequency",
                           "Pro-KWo")


figure2S_data <-  Figure2S_data %>% 
  gather(key = "Predictor", value =  "Predictor Value",`Lexical Diversity`:`Pro-KWo`)

figure2S_data$Predictor = factor(figure2S_data$Predictor, 
                                levels=c("Frequency","Lexical Diversity",
                                         "Document Diversity","Pro-KWo"))

#create plot
age_Predictor_Matrix.plot_ALL <- figure2S_data %>% 
  ggplot(aes(x = `Predictor Value`,y = MCDIp, color = Predictor)) + 
  geom_point(shape = 1)

#set rows
age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL + 
  facet_grid(rows = vars(age))

#set columns
age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL + 
  facet_grid(cols = vars(Predictor))

#complete matrix
age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL + 
  facet_grid(vars(age),vars(Predictor),scales = "free_x")

#add theme
age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL + theme_bw() + 
  theme(legend.position= "none",
        text = element_text(size=30, face = "bold", hjust = 0.5)) 


age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL+ 
  scale_color_manual(values = c("#eeb1a2","#02a699","#f45c51","#274dc6")
)

age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL +
    theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank() ,
        panel.spacing.x = unit(1.5,"lines"), 
        plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#00539CFF" ) ,
        strip.text = element_text(colour = "#FFD662FF" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA), 
        text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold"))  + 
  geom_smooth(method=lm, se=TRUE, show.legend = TRUE, fill = "lightgray") + 
  ylim(0,1)

age_Predictor_Matrix.plot_ALL <- age_Predictor_Matrix.plot_ALL + 
  stat_cor(method = "pearson", color = "black",size = 7,digits = 2,
    
    #label.x.npc = "bottom", 
    #label.y.npc = "right", 
    
    )

ggsave(age_Predictor_Matrix.plot_ALL,
       file = here("supplemental material","Figure 2S. MCDIp by Predictor and ALL age.png"),dpi = "retina",width = 15, height = 19)
```

## Figure 4. MCDIp Scores at 24 months Across Grammatical Class.

```{r, Correlogram}
#Our transformation function
scaleFUN <- function(x) sprintf("%.2f", x)

#use only variables to be correlated
Figure4_data <- plotting_dataset %>% filter(age == 24) %>% select(word,lexical_class,log_FQ,LD,DD,PKC)

colnames(Figure4_data) <- c("Word","Lexical_Class","Frequency","Lexical Diversity","Document Diversity","Pro-KWo")

levels(Figure4_data$Lexical_Class) <- c("Adjective","Function","Noun", "Verb")

#plot

Figure4_data <- ggpairs(Figure4_data,columns= c("Frequency","Lexical Diversity","Document Diversity","Pro-KWo"),
              mapping=ggplot2::aes(colour = Lexical_Class, fontface = "bold"),
              upper = list(continuous = wrap('cor', size = 8, alpha = 0.9)))  + theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank() ,
        plot.title = element_text(hjust = 0.5),
        panel.spacing.x = unit(1.5,"lines"),
        strip.background = element_rect(fill = "#00539CFF" ) ,
        strip.text = element_text(colour = "#FFD662FF" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA), 
        text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 20, face = "bold")) 



for(i in 1:Figure4_data$nrow) {
  for(j in 1:Figure4_data$ncol){
    Figure4_data[i,j] <- Figure4_data[i,j] + 
        scale_fill_manual(values=c("#FFB449","#6fafc7","#bfd46d","#ee5e5e")) +
        scale_color_manual(values=c("#FFB449","#6fafc7","#bfd46d","#ee5e5e"))  
  }
}



ggsave(plot = Figure4_data,file= here("figures_&_tables","Figure 4. Correlogram with Grammatical Class 24.png"), width = 15 , height = 15)
```

## Figure 5. MCDIp Scores at 24 months label.
```{r, reshape_figure2}
Figure5_data <- plotting_dataset %>% filter(age == 24) %>% select(MCDIp,word,lexical_class,log_FQ,LD,DD,PKC)

colnames(Figure5_data) <- c("MCDIp","Word","Lexical_Class","Frequency","Lexical Diversity","Document Diversity","Pro-KWo")

Figure5_data$MCDIp <- as.factor(Figure5_data$MCDIp)

Figure5_data.melt <- melt(Figure5_data, by = c("Word","Lexical Class","MCDIp"))

# Treat MCDIp as numeric
Figure5_data.melt$MCDIp <- as.numeric(as.character(Figure5_data.melt$MCDIp))
```

```{r, square}
#plot 
Label_Plot.24 <-Figure5_data.melt %>%  
  ggplot(aes(x=value, y= MCDIp, fill = Lexical_Class)) 

Label_Plot.24 <- Label_Plot.24 + geom_label(aes(label = Word), 
                                            label.size = 0.01) 

Label_Plot.24 <- Label_Plot.24 + 
  scale_fill_manual(labels =c("Adjectives","Function", "Nouns","Verbs"), 
                    values = c("#ffd125","#6fafc7","#bfd46d","#ee5e5e")
)

Label_Plot.24<- Label_Plot.24 + 
  facet_wrap(~ variable, scales = "free", ncol = 2, nrow = 2) + theme_bw() 

Label_Plot.24<- Label_Plot.24  + 
  theme(text = element_text(size=20, face = "bold", hjust = 0.5), 
        legend.position = "top", legend.title = element_blank(), 
        axis.title.x=element_blank()) 


Label_Plot.24<- Label_Plot.24 + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank() ,
        plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#00539CFF" ) ,
        strip.text = element_text(colour = "#FFD662FF" ) ,
        panel.border = element_rect(color = "steelblue", size = 1, fill = NA), 
        text = element_text(size=28, face = "bold", hjust = 0.5), 
        axis.text.x = element_text(size = 17, face = "bold"),
        axis.text.y = element_text(size = 17, face = "bold")) 

# Set the y-axis to range from 0 to 1
#Label_Plot.24 <- Label_Plot.24 + ylim(0, 1)

ggsave(Label_Plot.24, file = here("figures_&_tables","Figure 5. MCDIp Scores at 24 months.jpeg"), dpi = "retina", width = 17, height = 15)
```

## Figure 6. MCDIp Across Grammatical Class
### Calculate correlation within grammatical class
```{r, unique- compute_age.grouped}
figure6_data <-
  plotting_dataset %>% group_by(age) %>% mutate(
    all_freq = cor(MCDIp, log_FQ),
    all_ld = cor(MCDIp, LD),
    all_dd = cor(MCDIp, DD),
    all_pkc = cor(MCDIp, PKC)
  )
```

```{r, unique- compute_age_Lexical_Class_grouped}
figure6_data <-
  figure6_data %>% group_by(age, lexical_class) %>% mutate(
    lex_freq = cor(MCDIp, log_FQ),
    lex_ld = cor(MCDIp, LD),
    lex_dd = cor(MCDIp, DD),
    lex_pkc = cor(MCDIp, PKC)
  )

```

```{r}
#reshape in order to plot

figure6_data1<- melt(figure6_data, id=c("age","lexical_class"))
figure6_data1.5 <- unique(figure6_data1)

figure6_data2 <- filter(figure6_data1.5, 
 variable %in% 
   c('all_freq','all_ld','all_dd','all_pkc',"lex_freq","lex_ld","lex_dd","lex_pkc"))

figure6_data3 <- figure6_data2 %>% mutate(category = 
                                      case_when(grepl("all", variable) ~ "All",
                                  grepl("function", lexical_class) ~ "Function",
                                  grepl("verbs", lexical_class) ~ "Verbs",
                                  grepl("adjectives", lexical_class) ~ "Adjectives",
                                  grepl("nouns", lexical_class) ~ "Nouns"))

figure6_data4 <- figure6_data3 %>% mutate(Predictor = 
                                      case_when(grepl("freq", variable) ~ "Frequency",
                                  grepl("ld", variable) ~ "Lexical Diversity",
                                  grepl("dd", variable) ~ "Document Diversity",
                                  grepl("pkc", variable) ~ "Pro-KWo"))
                                                                     


```

```{r}
# Figure 6 Correlation Across 5 age groups.

figure6_data4$Predictor = factor(figure6_data4$Predictor , levels=c("Frequency","Document Diversity","Lexical Diversity","Pro-KWo"))
figure6_data4$value <- as.numeric(figure6_data4$value)

age_vector <- c(18,21,24,27,30)

figure6 <- ggplot(data=figure6_data4 %>% filter(age %in% age_vector),
            aes(x = age,y = value,color= category))+
    geom_line(aes(group = category), size = 2) +
    geom_point(aes(group = category), size = 2)+ facet_wrap(~ Predictor, nrow = 1)
                          

figure6 <- figure6 + labs( x = "age (mo)" , y = "Pearson correlation (r)", color = "Lexical Class")     

figure6 <- figure6 + scale_color_manual(labels =c("Adjectives","All","Function","Nouns","Verbs"), values = c("#ffd125","#000000","#6fafc7","#bfd46d","#ee5e5e"))


figure6 <- figure6 +  theme_bw() + theme(legend.position= "top",text = element_text(size=20, face = "bold", hjust = 0.5))

figure6 <- figure6 + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank() ,plot.title = element_text(hjust = 0.5),strip.background = element_rect(fill = "#00539CFF" ) ,strip.text = element_text(colour = "#FFD662FF" ) ,panel.border = element_rect(color = "steelblue", size = 1, fill = NA), text = element_text(size=22, face = "bold", hjust = 0.5), axis.text.x = element_text(size = 14, face = "bold"),axis.text.y = element_text(size = 14, face = "bold")) 


ggsave(figure6, file = here("figures_&_tables","Figure 6. Correlation of MCDI and Distributional  Statistics across 5 age groups for each word's grammatical class.jpeg"), width = 15, height = 8)
```

```{r, cross-sectional}

# Figure 6S Correlation Across all age groups.

figure6_data4$Predictor = factor(figure6_data4$Predictor , levels=c("Frequency","Document Diversity","Lexical Diversity","Pro-KWo"))
figure6_data4$value <- as.numeric(figure6_data4$value)



figure6S <- ggplot(data=figure6_data4,
            aes(x = age,y = value,color= category))+
    geom_line(aes(group = category), size = 2) +
    geom_point(aes(group = category), size = 2)+ facet_wrap(~ Predictor, nrow = 1)
                          

figure6S <- figure6S + labs( x = "age (mo)" , y = "Pearson correlation (r)", color = "Lexical Class")     

figure6S <- figure6S + scale_color_manual(labels =c("Adjectives","All","Function","Nouns","Verbs"), values = c("#ffd125","#000000","#6fafc7","#bfd46d","#ee5e5e"))


figure6S <- figure6S +  theme_bw() + theme(legend.position= "top",text = element_text(size=20, face = "bold", hjust = 0.5))

figure6S <- figure6S + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank() ,plot.title = element_text(hjust = 0.5),strip.background = element_rect(fill = "#00539CFF" ) ,strip.text = element_text(colour = "#FFD662FF" ) ,panel.border = element_rect(color = "steelblue", size = 1, fill = NA), text = element_text(size=22, face = "bold", hjust = 0.5), axis.text.x = element_text(size = 14, face = "bold"),axis.text.y = element_text(size = 14, face = "bold")) 


ggsave(p, file = here("supplemental material","Figure 6S. Correlation of MCDI and Distributional  Statistics across age for each word's grammatical class.jpeg"), width = 15, height = 8)
```



