---
title: "Inferentials"
output: html_document
---

# Load pckg
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(performance)
library(lme4)
library(lattice) 
library(ggplot2) 
library(stringi) 
library(gt)
library(data.table)
library(optimx)
library(sjPlot)
library(sjmisc)
library(broom)
library(progress)
library(progressr)
library(pbapply) 
library(here)

```


```{r}
#Create suplementary figure data file structure
data_folder <- here("R_Objects")
if (!dir.exists(data_folder)) {
  dir.create(data_folder)
}
```

# Load MCDI_CHILDES Dataset

```{r}
# Read in data
MCDI <- fread(here("data", "regression_dataset.csv"), colClasses = c("factor","numeric","factor","factor","numeric","numeric","numeric","numeric",
   "numeric"                                                                   ))
```


# Random Effects Models
## model1: produce ~ (1|subject)
```{r, empty_model1}
# Subset the data to include only the columns being used in the model
MCDI_model1 <- subset(MCDI, select = c("produce", "subject"))

# Fit an empty model with random intercept for subject using the "Nelder-Mead" optimizer
model1 <- glmer(produce ~ (1|subject), data = MCDI_model1, family = "binomial", control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE,optCtrl = list(maxfun = 100000)))

# Save model, summary, and performance
save(model1, file = here("R_Objects","model1.Rdata"))

```

## model2: produce ~ (1|word)
```{r, empty_model2}
# Subset the data to include only the columns being used in the model
MCDI_model2 <- subset(MCDI, select = c("produce", "word"))

# Fit an empty model with random intercept for word using the "bobyqa" optimizer
model2 <- glmer(produce ~ (1|word), data = MCDI_model2, family = "binomial", 
                 control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model, summary, and performance
save(model2, file = here("R_Objects", "model2.Rdata"))
```

## model3: produce ~ (1|age)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model3 <- subset(MCDI, select = c("produce", "age"))

# Fit an empty model with random intercept for age using the "bobyqa" optimizer
model3 <- glmer(produce ~ (1|age), data = MCDI_model3, family = "binomial", 
                 control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model, summary, and performance
save(model3, file = here("R_Objects", "model3.Rdata"))
```

### Compare empty models with single random effects
```{r compare empty model 1,2 and 3}
# Load the saved models
#load("model1.Rdata")
#load("model2.Rdata")
#load("model3.Rdata")

# Calculate AIC and BIC for each model
AICs <- sapply(list(model1, model2, model3), AIC)
BICs <- sapply(list(model1, model2, model3), BIC)

# Print the AIC and BIC values
print(AICs)
print(BICs)

# Find the model with the lowest AIC and BIC values
best_model_AIC <- which.min(AICs)
best_model_BIC <- which.min(BICs)

# Print the best model based on AIC and BIC values
cat("The best model based on AIC is model", best_model_AIC, "\n")
cat("The best model based on BIC is model", best_model_BIC, "\n")
```
The above table indicates the amount of variance explained by each grouping 
factor. This initial comparison allows us to rank models based on amount of
variance in word production explained (i.e 1.-subject , 2.-word , 3.-age)

# Empty models (2 random effects)
We can then ask to what extent do these grouping factors account for unique 
variance as opposed to shared. We account for this by comparing a 
model with just *subjects* as a random effect and see how adding *word* and 
*age* changes the R2.

## model4: produce ~ (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model4 <- subset(MCDI, select = c("produce", "subject", "word"))

# Fit an empty model with random intercepts for subject and word using the "bobyqa" optimizer
model4 <- glmer(produce ~ (1|subject) + (1|word), 
                data = MCDI_model4,
                family = "binomial", 
                control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model, summary, and performance
save(model4, file = here("R_Objects", "model4.Rdata"))

```

## model5: produce ~ (1|subject) + (1|age)
```{r}
# model5
model5 <- glmer(produce ~ (1|subject) + (1|age), 
                      data = MCDI,
                      family = "binomial", 
                control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# save model5 
save(model5, file = here("R_Objects", "model5.Rdata"))
```

## model6: produce ~ (1|age) + (1|word)
```{r}
# model6
model6 <- glmer(produce ~ (1|age) + (1|word), 
                      data = MCDI,
                      family = "binomial", 
                control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))


# save model6 
save(model6, file = here("R_Objects", "model6.Rdata"))

```

### Compare empty models with two random effects
```{r compare empty model 4,5 and 6}
# Calculate AIC and BIC for each model
AICs <- sapply(list(model4, model5, model6), AIC)
BICs <- sapply(list(model4, model5, model6), BIC)

# Print the AIC and BIC values
print(AICs)
print(BICs)

# Find the model with the lowest AIC and BIC values
best_model_AIC <- which.min(AICs)
best_model_BIC <- which.min(BICs)

# Print the best model based on AIC and BIC values
cat("The best model based on AIC is model", best_model_AIC, "\n")
cat("The best model based on BIC is model", best_model_BIC, "\n")
```

Empty model (3 random effects)
## model7: produce ~ (1|subject) + (1|word) + (1|age)
```{r}
# model7
model7 <- glmer(produce ~ (1|subject) + (1|word) + (1|age), 
                      data = MCDI,
                       family = "binomial", 
                control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# save model7 summary and performance
save(model7, file = here("R_Objects", "model7.Rdata"))
```
Comparing Model 7 to Model 4 shows that the addition of age as a grouping factor
does not improve model fit substantially: \newline 
(model4 R2 = 0.7782681 ; model7 R2 = 0.7794932) , given the importance of 
accounting for the grouping factors of *subject* and *word*, all subsequent 
models will include each as random effects.
# Single Predictor Models
## 18 
## model8.0: produce ~ Frequency + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model8 <- subset(MCDI, select = c("produce", "FQ_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for FQ_scaled 
model8.0 <- glmer(produce ~ FQ_scaled + (1|subject) + (1|word), 
                  data = MCDI_model8 %>% filter(age == "18"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

               
# save model8.0 summary and performance
save(model8.0, file = here("R_Objects", "model8.0.Rdata"))
```

## model8.1: produce ~ Lex_Diversity + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model8.1 <- subset(MCDI, select = c("produce", "LD_scaled", "subject", "word", "age"))


# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Lexical Diversity
model8.1 <- glmer(produce ~ LD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model8.1 %>% filter(age == "18"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model8.1, file = here("R_Objects", "model8.1.Rdata"))
```

## model8.2: produce ~ Doc_Diversity + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model8.2 <- subset(MCDI, select = c("produce", "DD_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Document Diversity
model8.2 <- glmer(produce ~ DD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model8.2 %>% filter(age == "18"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model8.2, file = here("R_Objects", "model8.2.Rdata"))
```

## model8.3: produce ~ Pro-KWo + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model8.3 <- subset(MCDI, select = c("produce", "PKC_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Pro-KWo
model8.3 <- glmer(produce ~ PKC_scaled + (1|subject) + (1|word), 
                  data = MCDI_model8.3 %>% filter(age == "18"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model8.3, file = here("R_Objects", "model8.3.Rdata"))
```

### Compare single predictor models with two random effects
```{r}
# Calculate AIC and BIC for each model
AICs <- sapply(list(model8.0, model8.1, model8.2,model8.3), AIC)
BICs <- sapply(list(model8.0, model8.1, model8.2,model8.3), BIC)

# Print the AIC and BIC values
print(AICs)
print(BICs)

# Find the model with the lowest AIC and BIC values
best_model_AIC <- which.min(AICs)
best_model_BIC <- which.min(BICs)

# Print the best model based on AIC and BIC values
cat("The best model based on AIC is model", best_model_AIC, "\n")
cat("The best model based on BIC is model", best_model_BIC, "\n")
```

## 21                                          
## model9.0: produce ~ Frequency + (1|subject) + (1|word)
```{r}
MCDI_model9.0 <- subset(MCDI, select = c("produce", "FQ_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Frequency
model9.0 <- glmer(produce ~ FQ_scaled + (1|subject) + (1|word), 
                  data = MCDI_model9.0 %>% filter(age == "21"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model9.0, file = here("R_Objects", "model9.0.Rdata"))
```

## model9.1: produce ~ Lex_Diversity + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model9.1 <- subset(MCDI, select = c("produce", "LD_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Lexical Diversity
model9.1 <- glmer(produce ~ LD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model9.1 %>% filter(age == "21"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model9.1, file = here("R_Objects", "model9.1.Rdata"))
```

## model9.2: produce ~ Doc_Diversity + (1|subject) + (1|word)
```{r}
# model9.2
# Subset the data to include only the columns being used in the model
MCDI_model9.2 <- subset(MCDI, select = c("produce", "DD_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Document Diversity
model9.2 <- glmer(produce ~ DD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model9.2 %>% filter(age == "21"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model
save(model9.2, file = here("R_Objects", "model9.2.Rdata"))
```

## model9.3: produce ~ Pro-KWo + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model9.3 <- subset(MCDI, select = c("produce", "PKC_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Pro-KWo
model9.3 <- glmer(produce ~ PKC_scaled + (1|subject) + (1|word), 
                  data = MCDI_model9.3 %>% filter(age == "21"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
```


### Compare single predictor models with two random effects 
```{r compare empty model 1,2 and 3}
compare_21_models<- compare_performance(model9.0, model9.1, 
                                        model9.2,model9.3) %>% 
  gt() %>% 
  tab_header(title = "Compare empty models with single random effect",
             subtitle = "model9.0 : produce ~ Frequency + (1|subject) + (1|word)
                         model9.1 : produce ~ Lex_Diversity + (1|subject) + (1|word),
                         model9.2 : produce ~ Doc_Diversity + (1|subject) + (1|word),
                         model9.3 : produce ~ Pro-KWo + (1|subject) + (1|word)")

save(compare_21_models, file = here("R_Objects", "Compare 21 month single models.Rdata"))
```

## 24
## model10.0: produce ~ Frequency + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model10.0 <- subset(MCDI, select = c("produce", "FQ_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Frequency
model10.0 <- glmer(produce ~ FQ_scaled + (1|subject) + (1|word), 
                  data = MCDI_model10.0 %>% filter(age == "24"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model10.0
save(model10.0, file = here("R_Objects", "model10.0.Rdata"))

```

## model10.1: produce ~ Lex_Diversity + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model10.1 <- subset(MCDI, select = c("produce", "LD_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Lexical Diversity
model10.1 <- glmer(produce ~ LD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model10.1 %>% filter(age == "24"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model10.1
save(model10.1, file = here("R_Objects", "model10.1.Rdata"))
```

## model10.2: produce ~ Doc_Diversity + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model10.2 <- subset(MCDI, select = c("produce", "DD_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Doc_Diversity
model10.2 <- glmer(produce ~ DD_scaled + (1|subject) + (1|word), 
                  data = MCDI_model10.2 %>% filter(age == "24"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))

# Save model10.2
save(model10.2, file = here("R_Objects", "model10.2.Rdata"))
```

## model10.3: produce ~ Pro-KWo + (1|subject) + (1|word)
```{r}
# Subset the data to include only the columns being used in the model
MCDI_model10.3 <- subset(MCDI, select = c("produce", "PKC_scaled", "subject", "word", "age"))

# Fit an empty mixed-effects logistic regression model with random intercepts for subject and word, and fixed effect for Pro-KWo
model10.3 <- glmer(produce ~ PKC_scaled + (1|subject) + (1|word), 
                  data = MCDI_model10.3 %>% filter(age == "24"),
                  family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
# Save model10.3
save(model10.3, file = here("R_Objects", "model10.3.Rdata"))
```

### Compare single predictor models with two random effects 
```{r compare empty model 1,2 and 3}
compare_24_models<- compare_performance(model10.0, model10.1, 
                                        model10.2,model10.3) %>% 
  gt() %>% 
  tab_header(title = "Compare empty models with single random effect",
             subtitle = "model10.0 : produce ~ Frequency + (1|subject) + (1|word)
                         model10.1 : produce ~ Lex_Diversity + (1|subject) + (1|word),
                         model10.2 : produce ~ Doc_Diversity + (1|subject) + (1|word),
                         model10.3 : produce ~ Pro-KWo + (1|subject) + (1|word)")

save(compare_24_models, file = here("R_Objects", "Compare 24 month single models.Rdata"))
```


## 27 
## model11.0: produce ~ Frequency + (1|subject) + (1|word)
```{r}
# model11.0
MCDI_model11.0 <- subset(MCDI, select = c("produce", "FQ_scaled", "subject", "word", "age"))
model11.0 <- glmer(produce ~ FQ_scaled + (1|subject) + (1|word), 
                      data = MCDI_model11.0 %>% filter(age == "27"),
                          family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
                                          
# save model11.0
save(model11.0, file = here("R_Objects", "model11.0.Rdata"))
```

## model11.1: produce ~ Lex_Diversity + (1|subject) + (1|word)
```{r}
# model11.1
MCDI_model11.1 <- subset(MCDI, select = c("produce", "LD_scaled", "subject", "word", "age"))
model11.1 <- glmer(produce ~ LD_scaled + (1|subject) + (1|word), 
                      data = MCDI_model11.1 %>% filter(age == "27"),
                         family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
                      
# save model11.1
save(model11.1, file = here("R_Objects", "model11.1.Rdata"))
```

## model11.2: produce ~ Doc_Diversity + (1|subject) + (1|word)
```{r}
# model11.2
MCDI_model11.2 <- subset(MCDI, select = c("produce", "DD_scaled", "subject", "word", "age"))
model11.2 <- glmer(produce ~ DD_scaled + (1|subject) + (1|word), 
                      data = MCDI_model11.2 %>% filter(age == "27"),
                          family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
                      
# save model11.2
save(model11.2, file = here("R_Objects", "model11.2.Rdata"))
```

## model11.3: produce ~ Pro-KWo + (1|subject) + (1|word)
```{r}
# model11.3
MCDI_model11.3 <- subset(MCDI, select = c("produce", "PKC_scaled", "subject", "word", "age"))
model11.3 <- glmer(produce ~ PKC_scaled + (1|subject) + (1|word), 
                      data = MCDI_model11.3 %>% filter(age == "27"),
                          family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl = list(maxfun = 100000)))
# save model11.3
save(model11.3, file = here("R_Objects", "model11.3.Rdata"))
```

### Compare single predictor models with two random effects 

```{r compare empty model 1,2 and 3}
compare_27_models<- compare_performance(model11.0, model11.1, 
                                        model11.2,model11.3) %>% 
  gt() %>% 
  tab_header(title = "Compare empty models with single random effect",
             subtitle = "model11.0 : produce ~ Frequency + (1|subject) + (1|word)
                         model11.1 : produce ~ Lex_Diversity + (1|subject) + (1|word),
                         model11.2 : produce ~ Doc_Diversity + (1|subject) + (1|word),
                         model11.3 : produce ~ Pro-KWo + (1|subject) + (1|word)")

save(compare_27_models, file = here("R_Objects", "Compare 27 month single models.Rdata"))
```
## 30 
## model12.0: produce ~ Frequency + (1|subject) + (1|word)

```{r}
# model12.0
model12.0 <- glmer(produce ~ FQ_scaled + (1|subject) + (1|word), 
                    data = subset(MCDI, age == "30", select = c("produce", "FQ_scaled", "subject", "word")), 
                    family = "binomial", 
                    control = glmerControl(optimizer = "Nelder_Mead"))
                      
# save model12.0
save(model12.0, file = here("R_Objects", "model12.0.Rdata"))

```

## model12.1: produce ~ Lex_Diversity + (1|subject) + (1|word)
```{r}
# model12.1
model12.1 <- glmer(produce ~ LD_scaled + (1|subject) + (1|word), 
                    data = subset(MCDI, age == "30", select = c("produce", "LD_scaled", "subject", "word")), 
                    family = "binomial", 
                    control = glmerControl(optimizer = "Nelder_Mead"))

# save model12.1
save(model12.1, file = here("R_Objects", "model12.1.Rdata"))

```

## model12.2: produce ~ Doc_Diversity + (1|subject) + (1|word)
```{r}
# model12.2
model12.2 <- glmer(produce ~ DD_scaled + (1|subject) + (1|word), 
                    data = subset(MCDI, age == "30", select = c("produce", "DD_scaled", "subject", "word")), 
                    family = "binomial", 
                    control = glmerControl(optimizer = "Nelder_Mead"))

# save model12.2
save(model12.2, file = here("R_Objects", "model12.2.Rdata"))

```

## model12.3: produce ~ Pro-KWo + (1|subject) + (1|word)
```{r}
# model12.3
model12.3 <- glmer(produce ~ PKC_scaled + (1|subject) + (1|word), 
                    data = subset(MCDI, age == "30", select = c("produce", "PKC_scaled", "subject", "word")), 
                    family = "binomial", 
                    control = glmerControl(optimizer = "Nelder_Mead"))

# save model12.3
save(model12.3, file = here("R_Objects", "model12.3.Rdata"))

```

# Two Predictor Models 
## 18
## model13: produce ~ Frequency + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model13
model13_subset <- MCDI %>% 
                  filter(age == "18") %>% 
                  select(produce, FQ_scaled, PKC_scaled, subject, word)

# Fit model13 using only the relevant columns
model13 <- glmer(produce ~ FQ_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model13_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model13
save(model13, file = here("R_Objects", "model13.Rdata"))
```

## 21
## model14: produce ~ Frequency + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model14
model14_subset <- MCDI %>% 
                  filter(age == "21") %>% 
                  select(produce, FQ_scaled, PKC_scaled, subject, word)

# Fit model14 using only the relevant columns
model14 <- glmer(produce ~ FQ_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model14_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model14 summary and performance
save(model14, file = here("R_Objects", "model14.Rdata"))

```

## 24
## model15: produce ~ Frequency + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model15
model15_subset <- MCDI %>% 
                  filter(age == "24") %>% 
                  select(produce, FQ_scaled, PKC_scaled, subject, word)

# Fit model15 using only the relevant columns
model15 <- glmer(produce ~ FQ_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model15_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model15 summary and performance
save(model15, file = here("R_Objects", "model15.Rdata"))
```

## 27
## model16: produce ~ Frequency + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model16
model16_subset <- MCDI %>% 
                  filter(age == "27") %>% 
                  select(produce, FQ_scaled, PKC_scaled, subject, word)

# Fit model16 using only the relevant columns
model16 <- glmer(produce ~ FQ_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model16_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model16 summary and performance
save(model16, file = here("R_Objects", "model16.Rdata"))
```

## 30
## model17: produce ~ Frequency + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model17
model17_subset <- MCDI %>% 
                  filter(age == "30") %>% 
                  select(produce, FQ_scaled, PKC_scaled, subject, word)

# Fit model17 using only the relevant columns
model17 <- glmer(produce ~ FQ_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model17_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model17 summary and performance
save(model17, file = here("R_Objects", "model17.Rdata"))
```

# Two Predictor Models 
## 18
## model18: produce ~ Lexical Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model18
model18_subset <- MCDI %>% 
                  filter(age == "18") %>% 
                  select(produce, LD_scaled, PKC_scaled, subject, word)

# Fit model18 using only the relevant columns
model18 <- glmer(produce ~ LD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model18_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model18 summary and performance
save(model18, file = here("R_Objects", "model18.Rdata"))
```


## 21
## model19: produce ~ Lexical Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model24
model24_subset <- MCDI %>% 
                  filter(age == "21") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model24 using only the relevant columns
model24 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model24_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model24 summary and performance
save(model24, file = here("R_Objects", "model24.Rdata"))
```

## 24
## model20: produce ~ Lexical Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model20
model20_subset <- MCDI %>% 
                  filter(age == "24") %>% 
                  select(produce, LD_scaled, PKC_scaled, subject, word)

# Fit model20 using only the relevant columns
model20 <- glmer(produce ~ LD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model20_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model20 summary and performance
save(model20, file = here("R_Objects", "model20.Rdata"))

```

## 27
## model21: produce ~ Lexical Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model21
model21_subset <- MCDI %>% 
                  filter(age == "27") %>% 
                  select(produce, LD_scaled, PKC_scaled, subject, word)

# Fit model21 using only the relevant columns
model21 <- glmer(produce ~ LD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model21_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model21 summary and performance
save(model21, file = here("R_Objects", "model21.Rdata"))

```

## 30
## model22: produce ~ Lexical Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model22
model22_subset <- MCDI %>% 
                  filter(age == "30") %>% 
                  select(produce, LD_scaled, PKC_scaled, subject, word)

# Fit model22 using only the relevant columns
model22 <- glmer(produce ~ LD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model22_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model22 summary and performance
save(model22, file = here("R_Objects", "model22.Rdata"))
```

# Two Predictor Models 
## 18
## model23: produce ~ Document Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model23
model23_subset <- MCDI %>% 
                  filter(age == "18") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model23 using only the relevant columns
model23 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model23_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model23 summary and performance
save(model23, file = here("R_Objects", "model23.Rdata"))
```


## 21
## model24: produce ~ Document Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model24
model24_subset <- MCDI %>% 
                  filter(age == "21") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model24 using only the relevant columns
model24 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model24_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model24 summary and performance
save(model24, file = here("R_Objects", "model24.Rdata"))
```

## 24
## model25: produce ~ Document Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model25
model25_subset <- MCDI %>% 
                  filter(age == "24") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model25 using only the relevant columns
model25 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model25_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model25 summary and performance
save(model25, file = here("R_Objects", "model25.Rdata"))
```

## 27
## model26: produce ~ Document Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model26
model26_subset <- MCDI %>% 
                  filter(age == "27") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model26 using only the relevant columns
model26 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model26_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model26 
save(model26, file = here("R_Objects", "model26.Rdata"))
```

## 30
## model27: produce ~ Document Diversity + Pro-KWo + (1|subject) + (1|word) 
```{r}
# Subset columns needed for model27
model27_subset <- MCDI %>% 
                  filter(age == "30") %>% 
                  select(produce, DD_scaled, PKC_scaled, subject, word)

# Fit model27 using only the relevant columns
model27 <- glmer(produce ~ DD_scaled + PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model27_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model27 summary and performance
save(model27, file = here("R_Objects", "model27.Rdata"))

```

# Interaction models (age * Predictor)

## model28: produce ~ age * Frequency + (1|subject) + (1|word)
```{r, model28}
# Subset columns needed for model28
model28_subset <- MCDI %>% 
                  select(produce, FQ_scaled, age, subject, word)

model28 <- glmer(produce ~ FQ_scaled * age + 
                 (1|subject) + (1|word),
                 data = model28_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=5000)))



# Save model28 summary and performance
save(model28, file = here("R_Objects", "model28.Rdata"))
```

## model29: produce ~ age * Lexical Diversity + (1|subject) + (1|word)
```{r, model29}
# Subset columns needed for model29
model29_subset <- MCDI %>% 
                  select(produce, LD_scaled, age, subject, word)

# Fit model29 using only the relevant columns
model29 <- glmer(produce ~ LD_scaled * age + 
                 (1|subject) + (1|word),
                 data = model29_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model29 summary and performance
save(model29, file = here("R_Objects", "model29.Rdata"))
```

## model30: produce ~ age * Document Diversity + (1|subject) + (1|word)
```{r, model30}
# Subset columns needed for model30
model30_subset <- MCDI %>% 
                  select(produce, DD_scaled, age, subject, word)

# Fit model30 using only the relevant columns
model30 <- glmer(produce ~ DD_scaled * age + 
                 (1|subject) + (1|word),
                 data = model30_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model30 summary and performance
save(model30, file = here("R_Objects", "model30.Rdata"))
```

## model31: produce ~ age * Pro-KWo + (1|subject) + (1|word)
```{r, model31}
# Subset columns needed for model31
model31_subset <- MCDI %>% 
                  select(produce, PKC_scaled, age, subject, word)

# Fit model31 using only the relevant columns
model31 <- glmer(produce ~ PKC_scaled * age + 
                 (1|subject) + (1|word),
                 data = model31_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model31 summary and performance
save(model31, file = here("R_Objects", "model31.Rdata"))
```

# Model 32 : produce ~ Pro-KWo + (1|subject) + (1|word) at 24 months
```{r, model32}
# Subset columns needed for model32
model32_subset <- MCDI %>% 
                  filter(age == "24") %>% 
                  select(MCDIp,produce, PKC_scaled, subject, word)

# Fit model32 using only the relevant columns
model32 <- glmer(produce ~ PKC_scaled + 
                 (1|subject) + (1|word),
                 data = model32_subset,
                 family = "binomial", 
                 control = glmerControl(optimizer = "Nelder_Mead"))

# Save model32 summary and performance

save(model32, file = here("R_Objects", "model32.Rdata"))
```
# THE END