---
title: "Data Acquisition"
author: "Andrew.Z.Flores"
date: "4/10/2020"
output: html_document
---

```{r, packages}
# Uncomment to install
#install.packages("wordbankr")    
#install.packages("childesr")
```

```{r, libraries}
library(wordbankr) # required to download mcdi forms
library(childesr)  # required to download CHILDES transcripts
library(tidyverse)
```

# Data Acquisition
## Child Vocabulary Data
### Mac Arthur Bates Communicative Inventories (MCDI)
We will begin by downloading all English (American) "Words & Sentences" 
inventories from wordbank by using the *wordbankr* package and saving the 
dataset in its raw form.

```{r, download_mcdi}
# Download MCDI
get_mcdi <-
  get_instrument_data("English (American)",
                      "WS",
                      administrations = TRUE,
                      iteminfo = TRUE)
```

### Child Language Data Exchange System (CHILDES)
Next we will download all English (American) transcripts using the *childesr* 
package. This is a large file and make take 5 minutes or so to download.
```{r, download_childes}
# Download CHILDES utterances
childes_utterance <- get_utterances(collection = "Eng-NA")
```

```{r, select_columns}

#
select_mcdi <- get_mcdi %>% select(data_id,
                                   value,
                                   age,
                                   definition,
                                   type,
                                   lexical_class,
                                   lexical_category)

select_childes <- childes_utterance %>% select(id,
                                               target_child_age,
                                               gloss,
                                               type,
                                               speaker_code,
                                               speaker_role,
                                               speaker_code,
                                               collection_name,
                                               transcript_id)
```


```{r, save_files}
write.csv(childes_utterance, file = "|1|raw_childes.csv", row.names = FALSE)
write.csv(get_mcdi, file = "|1|raw_mcdi.csv", row.names = FALSE)
write.csv(select_childes, file = "|1|select_childes.csv", row.names = FALSE)
write.csv(select_mcdi, file = "|1|select_mcdi.csv", row.names = FALSE)
```

